SI: Settlements / Pottery traditions

### 2022-06-23 analysis/traditions/traditions.Rmd
add separate reports for various time resolutions
analysis for pottery traditions

@@

```{r spat-out}
set_spat %>% 
  select(id) %>% 
  inner_join(classif, by = "id") %>% 
  write_sf(here::here("analysis/traditions/traditions.geojson"), delete_layer = TRUE)
```

>>>>

```{r pca-summations}
loadings_sum <- pca_per %>% 
  summarise_variables()
```

```{r pca-summations-tb}
loadings_sum %>% 
  mutate(r = (PC1 + PC2 + PC3 + PC4 + PC5)/(ncol(loadings_sum) - 1)) %>% 
  select(column, r) %>% 
  arrange(reg, desc(r)) %>% 
  knitr::kable()
```

@@

```{r spat-out}
# set_spat %>% 
#   select(id) %>% 
#   inner_join(classif, by = "id") %>% 
#   write_sf(here::here("analysis/traditions/traditions.geojson"), delete_layer = TRUE)
```
